Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-05-11 doc/report/msc-report.tex
doc/report/msc-report.tex: only one quote in Implementation section.

The classic trade-off between time and space applys to wether or not
pre-compute an aggregate. Pre-computing to many aggregates might render an
unfeasible of data amount to store, while pre-computing to few aggregates
renders longer access times for aggregates which are not pre-computed. This
problem is further discussed in the thesis, but left to the user of the
Zohmg system to solve.

@@

%\chapterquote{A good idea is about ten percent and implementation and hard
%work, and luck is 90 percent.}{Guy Kawasaki}

\chapterquote{It is not always what we know or analyzed before we make a
decision that makes it a great decision. It is what we do after we make the
decision to implement and execute it that makes it a good
decision.}{William Pollard}

@@

The reducer, then, is very simple: it's a simple sum of the values. The output
of the reducer will not be stored on disk as is usually the case, but will
instead be interpreted by a custom OutputReader that persists the data to
HBase.

@@

\chapterquote{Example is not the main thing in influencing others, it's
the only thing}{Albert Schweitzer}

>>>>

The classic trade-off between time and space applies to whether or not
pre-compute an aggregate. Pre-computing to many aggregates might render an
unfeasible amount of data to store, while pre-computing to few aggregates
renders longer access times for aggregates which are not pre-computed. This
problem is further discussed in the thesis, but left to the user of the
Zohmg system to solve.

@@

\chapterquote{A good idea is about ten percent and implementation and hard
work, and luck is 90 percent.}{Guy Kawasaki}

%\chapterquote{It is not always what we know or analyzed before we make a
%decision that makes it a great decision. It is what we do after we make the
%decision to implement and execute it that makes it a good
%decision.}{William Pollard}

@@

The reducer, then, is very simple: it is a simple sum of the values. The output
of the reducer will not be stored on disk as is usually the case, but will
instead be interpreted by a custom OutputReader that persists the data to
HBase.

@@

\chapterquote{Example is not the main thing in influencing others, it's
the only thing.}{Albert Schweitzer}
